Paradigms in Physics 2.0

### 2017-06-13 paper.tex
pretty figure and edits from Corinne and Henri
start outlining new courses

\begin{figure*}
\includegraphics[width=\textwidth]{schedule}
\caption{Hypothetical student schedule for a student entering without
  calculus.  Students with AP Calculus can take the junior-year
  courses one year earlier, and students who start calculus-based
  physics in the Fall of their second year are not
  delayed.\label{schedule}}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{schedule}
\caption{Hypothetical student schedules for (a) a student entering
  without calculus and (b) a transfer student.  The Dependencies
  between courses are noted with arrows.  The area of each course is
  proportional to the credit value of the course, with the exception
  of math courses, which are shown in small boxes even though they are
  4-credit courses.\label{schedule}}
\end{figure*}
